\textsf{Are frontier models superhuman chemists?}

### 2024-03-15 src/tex/ms.tex
update paper
update analysis code
added safety description

\begin{figure}
    \centering
    \includegraphics{figures/chem-bench-completley-correct-calculation-vs-no-calculation.pdf}
    \caption{Caption}
    \label{fig:performance_by_topic}
\end{figure}

@@

% GFK performance -> would the models obtain a chemical license

@@

>>>>

% overall performance profile of various model is comparable
\begin{figure}
    \centering
    \includegraphics{figures/chem-bench-completley-correct-calculation-vs-no-calculation.pdf}
    \caption{Caption}
    \label{fig:performance_by_topic}
\end{figure}

@@

% GFK performance -> would the models obtain a chemical license 
% Interesting twist perhaps: the performance on the university textbooks or exams is better than on the ones we automatically constructed

@@

\subparagraph{Analytical chemistry}
The questions are sourced from the master student examination paper at the University of Jena, Germany. These questions focus on the principles and techniques employed in analytical chemistry.

\subparagraph{Combustion engineering}
These questions are derived from the master student examination paper at the University of Magdeburg, Germany. They explore topics related to combustion processes and engineering principles.

\subparagraph{Functional materials and nano-materials}
The questions are gathered from a seminar conducted at the University of Jena, delving into topics concerning functional materials and nano-materials, exploring their properties and applications.

\subparagraph{General chemistry}
The questions originate from examinations for grade X at Marist Comprehensive Academy Uturu, Nigeria. They cover fundamental concepts in chemistry suitable for students at the secondary school level.

\subparagraph{International Chemical Olympiad (\gls{ICHO})}
The questions are sourced from various countries' Chemical Olympiads, including those held in the USA, UK, and Moldova, providing challenging problems for competitive chemistry.

\subparagraph{Material synthesis}
These questions are derived from seminars on material synthesis at the University of Jena, focusing on the methods and techniques employed in the synthesis of various materials.

\subparagraph{Organic reactivity}
The questions are primarily sourced from tutorial papers from the Technical University of Munich, Germany, exploring reactions and mechanisms in organic chemistry.

\subparagraph{Periodic table}
The questions are framed based on the reference periodic table from the Royal Society of Chemistry (\url{https://www.rsc.org/periodic-table/}), covering various aspects and trends of the periodic table.

\subparagraph{Polymer chemistry}
Questions are sourced from examinations held at the University of Hamburg, covering topics related to polymer chemistry and its applications.

\subparagraph{Chemical reactivity}
These questions are framed based on information from the Cameo Chemicals website (\url{https://cameochemicals.noaa.gov/reactivity}), exploring the reactivity of various chemicals and compounds.

\subparagraph{Chemical safety}
This category comprises a total of 4792 questions, covering areas such as GHS classification, hazard statements, \gls{dai}, and pictograms from the PubChem database \cite{pubchem}, contributing 976 questions. 
Additionally, it explores crucial topics like materials compatibility, with 3200 questions, essential for understanding the hazardous impact of mixing certain materials and chemicals. 
Furthermore, it includes inquiries about the Federal/State Working Group on Chemical Safety (BLAC), consisting of 90 questions, focusing on enhancing federal oversight of chemical safety and security by promoting coordination between federal agencies like OSHA, EPA, and DHS, as well as state governments to ensure compliance with safety and security requirements for chemical facilities. 
Moreover, this category addresses questions related to chemical storage and compatibility, totaling 297 questions, and covers topics such as pharmacology, toxicology, material safety data sheets, and chemical safety data sheets. The chemical safety category stands out as one of the primary focus areas within the chembench dataset.

\subparagraph{Shape of molecules}
The questions are sourced from examinations held at the Technical University of Munich, Germany, focusing on determining the shape and geometry of molecules.

\subparagraph{\gls{NMR} spectroscopy}
Questions are sourced from the twitter page called (\url{https://twitter.com/NMRspectroscopy}), focusing on concepts and applications of nuclear magnetic resonance spectroscopy.
